\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{marvosym}

\begin{document}

\part{Stephen Bailey}

\section{Data Science and Programming}

\begin{eventlist}


\item{2017}
     {Center for Technology Transfer at Vanderbilt}
     {Application Developer}  
     
    \textbf{Developed core application for patent-pending "text readability" algorithm in Python.} 
    \newline

\begin{factlist}
    \item{$\bullet$}
         {Applied \textit{natural language processing} tools to decode and tokenize documents.}
         
    \item{$\bullet$}
         {Developed production Django web application to score and analyze documents, now used by lab researchers.}
\end{factlist}



\smallskip

\item{2017}
     {Metro Nashville Public Schools}
     {Data Analyst}

    \textbf{Built interactive reports on teacher vacancies that transformed communication between central office staff and 130+ school leaders.} \href{https://app.powerbi.com/view?r=eyJrIjoiZWVhMmIxMjUtOGM1Yi00MzQ4LWE4M2UtMzVlODA4N2NkNTVmIiwidCI6ImM2ODI4MjU3LTY0MTAtNDA3ZS1iNTU3LWI1ZGM3MjExZGU1NSIsImMiOjN9}{\color{blue}\Mundus}
    \newline

\begin{factlist}
    \item{$\bullet$}
        {Honed communication skills with multiple audiences, including executive leadership.}

\end{factlist}

\smallskip

\item{2013 -- Present}
     {Vanderbilt Brain Institute}
     {NIH Research Fellow}  
     
     \textbf{Used graph theory to model the human brain "connectome" and its importance for language.} 
     \newline

\begin{factlist}
    \item{$\bullet$}
         {Leveraged high performance computing cluster to streamline analyses, reducing human wait time from \textgreater 1 week to \textless 1 hour.}
         
    \item{$\bullet$}
         {Upgraded lab imaging database of 13,000+ scans by directing its migration to web-based storage platform (XNAT).}
         
    \item{$\bullet$}
         {Published analyses using machine learning to classify patients by disability based on MRI data. Also published papers with other methods, including GLM, ICA/PCA, graph theory, and time-series analysis.}
         
\end{factlist}


\smallskip

\item{2018 -- Present}
     {Nashville Biosciences}
     {Data Science Intern}

    \textbf{Built standardization pipelines for electronic health records from Vanderbilt's BioVU database.}
    \newline

\begin{factlist}
    \item{$\bullet$}
        {Mapped pharamaceutical data to NIH RxNorm database to allow matching across hundreds of different encoding schemes.}
\end{factlist}


\end{eventlist}


%%%%%%%%%
%%%%%%%%%

\personal
    [stkbailey.github.io]
    {\textbf{Overview\newline} I am a rigorous scientist with expertise in image processing and statistics, with a process-driven, engineering mindset. \smallskip\newline  Expect me to: Take ownership. Drive towards results. Put team first. Always ask questions. Improve every day.}
    {(615) 925-9322}
    {stkbailey@gmail.com}

\section{Education}

\begin{yearlist}

\item[Doctor of Philosophy]{2013 -- Pres.}
     {Neuroscience \& \newline Quantitative Methods}
     {Vanderbilt University}
\item[Bachelor of Science \newline Bachelor of Arts]{2007 -- 2011}
     {Chemistry \& Philosophy}
     {Samford University}
\end{yearlist}


\section{Technical Skills}

\begin{factlist}

\item{}
     {Python (esp. matplotlib, scikit-image, scikit-learn, keras), Ubuntu, bash,  Matlab, SQL, Power BI, HTML, Django, MS Office}

\end{factlist}


\section{Honors, Awards \& Talks}

\begin{factlist}
    
    \item{$\bullet$}
         {\textbf{Biomedical Image Analysis in Python}: Professionally-produced DataCamp.com online course. \href{https://www.datacamp.com/courses/biomedical-image-analysis-in-python}{\color{blue}\Mundus}} 
         
    \item{$\bullet$}
         {Accepted into the Insight Data Science Fellowship program.}
    
    \item{$\bullet$}
         {Awarded an National Institutes of Health research fellowship. \href{https://projectreporter.nih.gov/project_info_description.cfm?aid=9328269&icde=35806628}{\color{blue}\Mundus}}
         
    \item{$\bullet$}
        {\textbf{Deconvoluting Convolutions}: Recap of Kaggle's 2018 Data Science Bowl and tutorial on using deep convolutional networks for object detection.   \href{https://github.com/stkbailey/deconv-conv/blob/master/slides.pdf}{\textcolor{blue}\Mundus}}
     
    \item{$\bullet$}
        {\textbf{Principles of Network Analysis in Python}: Tutorial at PyTN on applying graph analysis to scraped data from Meetup.com. \href{https://github.com/stkbailey/nashnetx/blob/master/slides/PopularPythonistas_v3_PyTN.pdf}{\textcolor{blue}\Mundus}}
        
    \item{$\bullet$}
        {Research contributed to lab's latest NIH grant application, which scored in the 99th percentile and was awarded at \$2.5 million.}
         
    \item{$\bullet$}
         {Authored 8 papers, presented 9 posters and was invited to give a talk at a major international conference. \href{https://scholar.google.com/citations?user=s3nPF1MAAAAJ&hl=en}{\color{blue}\Mundus}}


\end{factlist}

\end{document}




%\item{May 2011 -- May 2013}
%     {Teach For America}
%     {Manager -- Regional Operations \newline Director -- Institute Technology}

%    \textbf{Tracked grant compliance, teacher development and business operations.} Built out reporting and compliance systems for \$120k AmeriCorps grant, and awarded a 55\% increase in funding (\$60k) after first year. Organized 15 professional development events attended by 60-120 professionals. Forecasted and tracked monthly business expenses for \$1,000,000+ operating budget. \newline
%    \textbf{Managed technology services for summer training institute}. Built out systems for providing IT support, printing and copying services for 800+ teachers. Direct manager of 4 full-time employees.  
